---
title: "E-Rate scratchpad 1"
output: html_notebook
---

 

```{r setup}
require(curl) #better downloads
require(data.table) #big data wrangling
require(magrittr) #use the pipe
require(stringr) #wrangle strings
require(assertr) #enforce expected outputs
require(here) #file path management (for now)
require(withr) #tempdir management 
require(dplyr) #binding rows
require(furrr) #simultinaeity
```

Resources:
- URL format for all: ` https://opendata.usac.org/resource/{identity}.csv` 
- All budgeted entities (C2 budget tool data): `6brt-5pbv` (initial sort)
- Emergency Connectivity Fund (USAC fun-to-have add-on): `i5j4-3rvr`
- Consultants: `g55z-erud` (also `x5px-esft` but the former appears slightly more complete?)
- Open competitive bidding: `jp7a-89nd` (includes *applicant type* field, can filter on)
- Consortia: `363f-22uh` (*consortium entity applicant type* can be filtered on)
- Services requested: `39tn-hjzv` (key is application number; contains category, entities served, what type of thing they want)
- Recipient details and commitments: `avi8-svp9` (key is application number; gestalt of other data sets and thus may or may not be desirable in itself)
- Discount request basic information: `9s6i-myen` (includes discount calculation data)
- Discount calculations: `upfy-khtr` (includes things not above; by application number)
- Connectivity information: `ym44-rnhq` (includes barriers, speeds)
- FRNs: `hbj5-2bpj` (includes purpose) 
- FRN status: `qdmp-ygft` (includes fiber types)
- Recipients of service: `tuem-agyq` (application-frn line alignment)
- Supplemental entity information: `7i5i-83qf` (feat. *parent + child type, parent type supersedes when needed if library system*)
```{r}
#test filtering by url
libraries <- 'https://opendata.usac.org/resource/6brt-5pbv.csv?applicant_type=Library&$limit=100000000'
lib_test <- curl::curl_download(url = libraries,
                                destfile = 'libtest.csv')
fread(file = lib_test)
#verified: this retrieves 4,347 results and USAC site expects the same.

lib_sys_test <- curl::curl_download('https://opendata.usac.org/resource/6brt-5pbv.csv?applicant_type=Library%20System&$limit=100000000', destfile = 'systest.csv')
fread(file = lib_sys_test)
#retrieves 1,448 library systems
#USAC site browser also currently expects 1,448 library systems
```

TODO: Figure out the Socrata bug re: passing tokens
TODO: Remember to use `sep2` fread parameter if needed

Filtering TODOs:
- determine if purpose is the only thing we want from that dataset and filter nulls if possible if so
- list of filterable by applicant type
- list of filterable by applicant type *or* parent type

Given nature of the filtered ones that have to be handled with multiple options, write to tempfile and extract and combine?

```{r}
curl::curl_download(url = 'https://opendata.usac.org/resource/6brt-5pbv.csv?applicant_type=Library&$limit=100000000',
                      destfile = 'lib.csv')
curl::curl_download(url = 'https://opendata.usac.org/resource/6brt-5pbv.csv?applicant_type=Library%20System&$limit=100000000',
                      destfile = 'sys.csv')
lib <- data.table::fread(file = 'lib.csv')
sys <- data.table::fread(file = 'sys.csv')
assertthat::are_equal(names(lib), names(sys)) #check that columns match 
libsys <- dplyr::bind_rows(lib, sys)
assertthat::are_equal((nrow(lib) + nrow(sys)),
                      nrow(libsys)) #check that the combined table contains rows from each 
```
```{r}
f <- \() {
  curl::curl_download(url = 'https://opendata.usac.org/resource/6brt-5pbv.csv?applicant_type=Library&$limit=100000000',
                      destfile = 'lib.csv')
  curl::curl_download(url = 'https://opendata.usac.org/resource/6brt-5pbv.csv?applicant_type=Library%20System&$limit=100000000',
                      destfile = 'sys.csv')
  lib <- data.table::fread(file = 'lib.csv')
  sys <- data.table::fread(file = 'sys.csv')
  assertthat::are_equal(names(lib), names(sys)) #check that columns match 
  libsys <- dplyr::bind_rows(lib, sys)
  assertthat::are_equal((nrow(lib) + nrow(sys)),
                      nrow(libsys)) #check that the combined table contains rows from each 
  libsys
}
```

```{r}
with_tempdir(f())
```

```{r}
build_usac <- \(dataset = '',
                by = NULL,
                accept = NULL) {
  
  if (is.null(by)) {
    res <- paste0('https://opendata.usac.org/resource/', dataset, '.csv?', '$limit=10000000') 
  } else {
    res <- paste0('https://opendata.usac.org/resource/', dataset, '.csv?', by, '_',
                  accept, '&$limit=10000000')
  }
  res
}

build_usac(dataset = '6brt-5pbv',
           by = 'applicant_type',
           accept = 'Library')
furrr::future_map_chr(.x = c('Library',
                             'Library%20System'),
                      .f = build_usac,
                      dataset = '6brt-5pbv',
                      by = 'applicant_type')
  #mapped version works 
```

